Pre-Main-Sequence M-Dwarfs With Complex Quasiperiodic Variability From Four Years of TESS

### 2023-06-20 paper/ms.tex
update ms with words

\paragraph{Effective temperatures, radii, and masses}
%TODO

@@

\paragraph{Connection to close-in exoplanets}
The concordance model for planet formation invokes the presence of an accretion
disk.
The disk is truncated (by what?) at the magnetospheric truncation radius,
which happens to often coincidentally be at the Keplerian corotation radius.
In such a scenario, planetesimals and boulders can migrate inward due to
Type X migration (CITE),
until they hit a ``dust trap'' at the inner wall.
Some support for this model comes from both the rotation periods of classical
and weak-lined T Tauri stars
(CITE Rebull2018,2019),
from near-infrared interferometric observations that detect thermal
emission from the disk wall (CITE CITE),
and from the turn-over in the exoplanet orbital period distribution,
which occurs around 5-10 days for FGK stars, 
and perhaps even closer-in for M-dwarfs (CITE Petigura2022, and CITE for M-dwarfs).

>>>>

\paragraph{Effective temperatures, radii, and masses}
%TODO
{\bf TODO}

@@

\paragraph{If the prominence scenario is correct, why don't stars in the
Hyades and Praesepe show the phenomenon?}

The prominence scenario, in a broad sense, argues that some intrinsic
stellar process is key for generating the CQV phenomenon.
If this were true, then stars of identical mass, size, and rotation
periods might be expected to show the phenomenon in equal number --
independent of age.
This is because the stellar dynamo for M-dwarfs is generated by fluid
motions inside the star, which should be identical for stars of the
same mass, size, and rotation period.

Between ages of $\approx$100\,Myr (AB Dor, Pleiades, Psc-Eri) and
$\approx$700\,Myr (Praesepe and Hyades), a 0.3\,M$_\odot$ star will
shrink by $\approx$10\%, from $\approx$0.33\,R$_\odot$ to 
$\approx$0.29\,R$_\odot$ (CITE MIST).
This is not a particularly drastic size change.
Similarly, many M-dwarfs  have similarly rapid rotation periods 
at 700\,Myr as they do at 100\,Myr (CITE Rebull2022); 
the mean population does show some evidence for spin-down after the
PMS contraction finishes, but a large fraction of the population is
still spinning more rapidly than the $\approx$2\,day limit at which
the CQV phenomenon becomes less common.

Broadly speaking -- the absence of old CQVs in our view seems to be
more plausibly linked to a gradual depletion of dusty detritus from the
planet formation era than it does to the changing stellar properties
as stars gradually finish their pre-main-sequence evolution, and then
continue to spin rapidly for many hundreds of millions of years.

\paragraph{Connection to close-in exoplanets}
The concordance model for planet formation invokes the presence of an accretion
disk.
The disk is truncated (by what?) at the magnetospheric truncation radius,
which happens to often coincidentally be at the Keplerian corotation radius.
In such a scenario, planetesimals and boulders can migrate inward due to
Type X migration (CITE),
until they hit a ``dust trap'' at the inner wall (CITE eg Kama2009,and
related).
Support for this model comes from the rotation periods of classical
and weak-lined T Tauri stars (CITE Rebull2018,2019);
from near-infrared interferometric observations that detect thermal
emission from the disk wall (CITE CITE);
and from the turn-over in the exoplanet orbital period distribution,
which occurs around 5-10 days for FGK stars, and perhaps even
closer-in for M-dwarfs (CITE Petigura2022, and CITE for M-dwarfs).

Broadly, the existence of a dust trap at the disk truncation radius 
might be expected to trap larger boulders as well.
Once the disk loses the gas, what happens to those boulders?
They are no longer shielded.
We then enter a phase of mass loss.
Perhaps that phase is what we are observing.
